### 2017-03-10 paper/oopsla17-submission/evaluation.tex
pretty graph

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
  ybar stacked,
  title={Spring 2014},
  ylabel={Accuracy},
  bar width=20pt,
  %ymin=0,
  ymax=1,
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\%},
  ymajorgrids = true,
  symbolic x coords={baseline, ocaml, mycroft, sherrloc,
                     op+type+size/linear, op+type+size/hidden-10,
                     op+type+size/hidden-500},
  % enlarge x limits=0.25,
  xtick=data,
  xticklabels={\baseline, \ocaml, \mycroft, \sherrloc,
               \linear, \hiddenT, \hiddenFH},
  x tick label style={rotate=45},
  reverse legend,
  legend style={legend pos = north west},
]
\addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\spring};
\addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\spring};
\addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\spring};
\legend{Top 1, Top 2, Top 3}
% \addplot[draw=black, fill=blue!20] table[col sep=comma, x=tool, y=top-1] {../../data/sp14/ocaml/results.csv};
% \addplot[draw=black, fill=blue!20] table[col sep=comma, x=tool, y=top-1] {../../data/sp14/mycroft/results.csv};
% \addplot[draw=black, fill=blue!20] table[col sep=comma, x=tool, y=top-1] {../../data/sp14/op+type+size/hidden-500/results.csv};
% \addplot[draw=black, fill=blue!40] table[col sep=comma, x=tool, y=top-2] {../../data/sp14/op+type+size/hidden-500/results.csv};
% \addplot[draw=black, fill=blue!60] table[col sep=comma, x=tool, y=top-3] {../../data/sp14/op+type+size/hidden-500/results.csv};
\end{axis}
\end{tikzpicture}

>>>>

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
  ybar stacked,
  width=12cm,
  height=8cm,
  title={Spring 2014},
  ylabel={Accuracy},
  bar width=20pt,
  ymin=0.2,
  ymax=1,
  yticklabel={\pgfmathparse{\tick*100}\pgfmathprintnumber{\pgfmathresult}\,\%},
  ytick style={draw=none},
  ymajorgrids = true,
  symbolic x coords={baseline, spacer1, ocaml, mycroft, sherrloc, spacer2,
                     op+type+size/linear, op+type+size/hidden-10,
                     op+type+size/hidden-500},
  % enlarge x limits=0.25,
  xtick=data,
  xtick style={draw=none},
  xticklabels={\baseline, \ocaml, \mycroft, \sherrloc,
               \linear, \hiddenT, \hiddenFH},
  x tick label style={rotate=45},
  reverse legend,
  legend style={legend pos = north west},
]
\addplot[draw=black, fill=blue1] table[x=tool, y=top-1] {\spring};
\addplot[draw=black, fill=blue2] table[x=tool, y expr=\thisrow{top-2} - \thisrow{top-1}] {\spring};
\addplot[draw=black, fill=blue3] table[x=tool, y expr=\thisrow{top-3} - \thisrow{top-2}] {\spring};
\legend{Top 1, Top 2, Top 3}
% \addplot[draw=black, fill=blue!20] table[col sep=comma, x=tool, y=top-1] {../../data/sp14/ocaml/results.csv};
% \addplot[draw=black, fill=blue!20] table[col sep=comma, x=tool, y=top-1] {../../data/sp14/mycroft/results.csv};
% \addplot[draw=black, fill=blue!20] table[col sep=comma, x=tool, y=top-1] {../../data/sp14/op+type+size/hidden-500/results.csv};
% \addplot[draw=black, fill=blue!40] table[col sep=comma, x=tool, y=top-2] {../../data/sp14/op+type+size/hidden-500/results.csv};
% \addplot[draw=black, fill=blue!60] table[col sep=comma, x=tool, y=top-3] {../../data/sp14/op+type+size/hidden-500/results.csv};
\end{axis}
\end{tikzpicture}
